Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/computation.tex
Working on 3 (almost done)

@@

\begin{figure}
  \centering
  \input{mean-distance.tikz}
  \caption{  \label{fig:meanvisibility-gridstep}. Mean distance of visibility as a function of the gridstep $h$.}
\end{figure}

>>>>

We have plotted on Fig.\ref{fig:meanvisibility-computationComplexity}
the running times to compute global visibility of both \cite[Algorithm
  3]{lachaud:2022-jmiv} and our algorithm. Timings are very
similar. Our algorithm is faster for smaller maximal radii (up to 20),
while the other is slightly faster for bigger radii. We have also
measured the (discrete) average visibility distance along digitization
of smooth shapes (Fig.~\ref{fig:meanvisibility-gridstep}). It follows
a law proportionnal to $\sqrt{h}$. As shown in the next section, for
real 3d images, a maximal radius below 10 is sufficient for normal and
curvature estimation.

@@

\begin{figure}
  \centering
  \input{mean-distance.tikz}
  \caption{\label{fig:meanvisibility-gridstep} Mean distance of visibility as a function of the gridstep $h$ (see text).}
\end{figure}
